---
title: "Progress So far"
author: "Kosuke Arai"
date: "10/8/2021"
header-includes:
   - \usepackage{multirow,slashbox,color}
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = F,warning = F,comment = "",eval=T)
source("rat.R")
dat <- read_csv("maindata3.csv")%>% filter(industry!="Non-manufacturing")
dat2 <- read_csv("masterdata.csv") %>% filter(industry!="Non-manufacturing") %>% rename(sales=investment)
stlis <- pim1(st=1978,ed=2018,real=T)
stlis2 <- pim1(t=45,d=0.1,st=1978,ed=2018,real=T)
```

# Motivation

\begin{itemize}
 \item Since the Industrial Revolution, from spinning machines to artificial intelligence, automation has affected firms and workers.
    \begin{itemize}
      \item Industrial Revolution made it worthwhile to bring workers under one roof (Mokyr (2001)).
      \item Around 47 percent of total US employment is expected to be automated relatively soon (Frey and Obsborne(2017)).
    \end{itemize}
\end{itemize}

I study the impact of industrial robots, such as assembly machines or packaging machines.

# Robot purchases by destination industry

```{r}
dat  %>% filter(industry!="Non-manufacturing") %>% ungroup() %>% group_by(industry,year) %>% mutate(sales=sum(sales,na.rm = T)) %>% slice_head() %>% 
  ggplot()+
  aes(year,log(sales),color=industry)+
  geom_line()+
  ylab(label = "log( Sales(million JPY) )")+
  scale_x_continuous(breaks = seq(1978,2018,10))+
  theme_bw()
```

# Sum of robot purchases 

```{r}
dat  %>% filter(industry!="Non-manufacturing") %>% ungroup() %>% group_by(year) %>% mutate(sales=sum(sales,na.rm = T)) %>% slice_head() %>% 
  ggplot()+
  aes(year,log(sales))+
  geom_line()+
  ylab(label = "log( Sales(million JPY) )")+
  scale_x_continuous(breaks = seq(1978,2018,10))+
  theme_bw()
```
 
# Robot stocks by industry

```{r}
ggplot(stlis)+
  aes(year,log(stock),color=industry)+
  geom_line()+
  scale_x_continuous(breaks = seq(1978,2018,10))+
  theme_bw()
```

# Sum of robot stocks

```{r}
ggplot(stlis %>% group_by(year) %>% mutate(stock=sum(stock)))+
  aes(year,log(stock))+
  geom_line()+
  scale_x_continuous(breaks = seq(1978,2018,10))+
  theme_bw()+
  geom_vline(xintercept = c(1978,1991),linetype="dashed")+
  annotate("rect",xmin=1994,xmax = 2018,ymin = 6,ymax = 12,alpha=0.2)
```

# Uniqueness

\begin{itemize}
 \item Detailed data of the shipments of industrial robots in Japan  
    \begin{itemize}
      \item Adachi et al. and Fujiwara et al. also study the impact of robots using this data. 
    \end{itemize}
    \item Focus on Firms.
    \begin{itemize}
      \item They above mainly study the impact on employments or wages. 
    \end{itemize}
\end{itemize}

How does automation changes manufacturing firms?

# Model - Hopenhayn and Rogerson (1993)

\begin{itemize}
\item Output and input prices $p_t$ and $w_t=1$ taken as given.
\item Productivity $s_t$ is stochastic and labor $n_t$ is the only input.
\begin{itemize}
\item The state of the economy is described by the distribution of \\$s_t$ and $n_t$, $\mu (s_t,n_t).$
\end{itemize}

\item A tax $\tau$ on job destruction.
\begin{itemize}
\item $g(n_t,n_{t-1})=\tau\ \cdot max[0,n_{t-1}-n_t]$
\end{itemize}
\end{itemize}

# Entry and Exit

\begin{itemize}
 \item At the start of each period, existing firms decide whether to remain in the market.
 \begin{itemize}
 \item If remain, they incur the fixed cost $p_t\cdot c_f$ and observe the current value of productivity, $s_t$.
 \item if exit, they pay $g(0,n_{t-1})$
 \end{itemize}
 \item At the start of each period, potential entrants (continuum) make decisions whether to enter.
 \begin{itemize}
 \item If enter, incur entry cost $p_t\cdot c_e$ and draw productivity $s_t$ from $v(s)$.
 \end{itemize}
\end{itemize}


# Incumbents' problem

- Consider stationary equilibrium with constant price $p$.  
- Let $W(s,n,p)$ denote value function for firms that had employment $n$ last period, that has decided to operate and drawn productivity $s$.  

- Bellman equation 
\begin{eqnarray*}
W(s,n;p)&=&\underset{n'\geq0}{max}\{ pf(n',s)-n'-pc_f-g(n',n) \\
& \qquad &+\beta\cdot max [E_sW(s',n';p),-g(0,n')] \}
\end{eqnarray*}

- Let $N(s,n,p)$ denote optimal employment policy and $X(s,n,p)\in\{0,1\}$ denote optimal exit policy ($X=1$ is exit.)
- Adjustment cost $r(s,n;p)$ is defined as;
\begin{eqnarray*}
r(s,n;p)&=&[1-X(s,n;p)]\int g(N(s',n;p),n)dF(s,s')\\
&\qquad& + X(s,n;p)\ \cdot g(0,n)
\end{eqnarray*}

# Entrants' problem

- Net value of entry

\[
W^e(p)=\int W(s,0;p)dv(s)-pc_e + pc_f
\]

- Let $m>0$ denote the mass of entrants, free entry condition implies;

\[
W^e(p)=0
\]

 - In Hopenhayn and Rogerson (1993), $W^e(p)$ is defined as $\int W(s,0;p)dv(s)-pc_e$. However, the footnote says entrants do not pay $pc_f$.

# Aggregation

- Aggregate output

\[
Y=\int [f(N(s,n;p),s)-c_f]d\mu(s,n)+M\int f(N(s,0;p),s)dv(s)
\]

- Labor demand

\[
L^d=\int N(s,n;p)d\mu(s,n)+M\int N(s,0;p)dv(s)
\]

 - Adjustment cost

\[
R=\int r(s,n;p)d\mu(s,n)
\]

 - Profit
 
 \[
\Pi=pY-L^d-R-Mpc_e
\]

# Consumers' problem

 - Representative consumer
 
 \[
\underset{N}{max}\ u(c)-aN \qquad s.t.\ pc\leq N+\Pi +R
\]

- Let $L^s(p,\Pi+R)$ denote the optimal labor supply, $N^*$.

# Stationary equilibrium conditions
 - $L^d(\mu^*,M^*,p^*)=L^s(p^*,\Pi^*+R^*)$
 - $T(\mu^*,M^*,p^*)=\mu^*$ where $T$ is the transition operator of $\mu$.
 - $W^e(p^*)=0$

# Specification

Mainly following Hopenhayn and Rogerson (1993) and Martin Floden (1997).

\begin{itemize}
\item$f(n,s)=sn^{0.64}$  
\item$g(n_t,n_{t-1})=0.2\times max[0,n_t-n_{t-1}]$  
\item$ln(s_t)=0.078+0.93\times ln(s_{t-1})+\epsilon_t \qquad \epsilon_t \sim N(0,0.0371) $  
\item Consumer's objective function $u(c)-aN=ln(c)-0.6N$  
\item$v(s)$ is uniform distribution on $[\underline{s},\underline{s}+0.65(\overline{s}-\underline{s})]$ where $[\underline{s},\overline{s}]$ is the span for incumbent firms.  
\item$c_f=12$
\item$c_e$ is determined so that $W^e(p)=0$ at $p=1$, as a result, 5.73.  
\end{itemize}


# Numerical Examples

VFI toolkit, made by Robert Kirkby, provides us the codes to run HR model.  
I adjusted them so that I can include $c_e$ as a parameter.

I assume automation heighten productivity and entry cost.

# Numerical Examples

\[
ln(s_t)=a+0.93\times ln(s_{t-1})+\epsilon_t 
\]

\begin{table}[h]
\caption{Average Firm Size}
\begin{tabular}{|c|c|c|c|}
\hline
\backslashbox{a}{$c_e$} & 5.73 & 6 & 15 \\
 \hline
0.078 & \textcolor{red}{23.81} & 24.56 & 69.96\\
\hline
0.1 & 14.35 & 15.19 & 42.21\\
\hline
 \end{tabular}
\end{table}

\begin{table}
\caption{Mass of Entrants}
\begin{tabular}{|c|c|c|c|}
\hline
\backslashbox{a}{$c_e$} & 5.73 & 6 & 15 \\
 \hline
0.078 & \textcolor{red}{0.0048} & 0.0047 & 0.0011\\
\hline
0.1 & 0.0081 & 0.0076 &0.0018\\
\hline
 \end{tabular}
 \end{table}

# Emprical Analysis

I adopt two main data

\begin{itemize}
\item Robot Shipments
\begin{itemize}
\item Made by Japan Robot Association (JRA). From 1978 to 2018.
\end{itemize}
\item Firms' numbers and their employment.
\begin {itemize}
\item Made by Prime Minister's office for 1978.\\
Made by Ministry of Economy, Trade and Industry from 1994 to 2018.
\end{itemize}
\end{itemize}

# JRA Data

\begin{table}[hbtp]
\begin{tabular}{|c|ccc|}
\hline
 & Assembling & Welding & Painting \\
\hline
 & 10 & 15 & - \\
Transport Machines & 140 & 200 & 10 \\
 \hline
 & 5 & 8 & 4 \\
Electric Machines & 20 & 40 & 30 \\
\hline
\end{tabular}
\end{table}

# Aggregate robot purchases

Following Adachi et al.(2020), I aggregate robot purchases as follows;
\[
R_{it}=\prod_a (R_{ait})^{\iota_{ai}} 
\]
where $R$ denotes the quantity of robots, $i$ indicates industry, $t$ indicates year, and $a$ indicates robot application.  
\smallskip
The aggregation weight $\iota_{ai}$ is constant over time and calculated as
\[
\iota_{ai}=\frac{v^A_{ai}}{\sum_a v^A_{ai}}
\]
where $v^A_{ai}$ is the average sales value of application $a$ to industry $i$ from 1978 to 2018.

# What is the $quantity\ of\ robots$?

1. Robot amount purchased in year $t$  
2. Robot amount purchased in year $t$   
$\qquad +$ (depreciated) past purchases  
3. Robot sales value$_{a,i,t}$ / Average robot prices$_{a,t}$  
4. Robot sales value$_{a,i,t}$ / Average robot prices$_{a,t}$  
$\qquad +$ (depreciated) Sales$_{a,i,t-1}$ / Average prices$_{a,t-1}\ + \cdots$  

\medskip
If I choose 1 or 3, I must sum up $R_{it}$ to make robot stocks,  
otherwise $R_{it}$ itself is the robot stock.  
I mainly use 3.  

# Robot price indicator

Following Adachi et al.(2020), I calculate robot price indicator as follows;
\[
r_{it}=\prod_a (r_{at})^{\iota_{ai}} 
\]
where $r_{at}$ is the average unit price for each application and year and  
$\iota_{ai}$ is the average expenditure share on application $a$ in industry $i$.

# Life length and depriciation rate

Adachi et al.(2020) and IFR set the life length of robots equals to 12 and depreciation rate equals to 0.  
Graetz and Michaels (2018) and Arai, Fujiwara and Shirota(2021) set life length infinity and depreciation rate 0.1.  

I adopt both method.  
Call stocks made in the first way "IWM stock" and  
ones made in the second way "PIM stock".  
\begin{eqnarray*}
IWM\ stock_{it} &=& \sum_{\tau\in[t-11,t]} R_{it} \\
PIM\ stock_{it} &=& \sum_{\tau\in[0,t]} (1-0.1)^{t-\tau} R_{it}
\end{eqnarray*}

# Industrial Analysis

Similar with Acemogle and Restrepo(2020), I do cross sectional analysis on the changes of some values between before and after industrial robots adopted, 1978 to 2018.  

```{r,out.height="75%"}
stlis %>% group_by(year) %>% mutate(istock=sum(stock)) %>% ungroup() %>% 
ggplot()+
  geom_line(aes(year,log(istock)),alpha=0.4,size=3)+
  geom_line(data=(stlis2 %>% group_by(year) %>% mutate(pstock=sum(stock)) %>% ungroup()),
            aes(year,log(pstock)),alpha=0.4,size=3,color="red")+
  labs(title = "Gray: ln(IWM stock)                 Red: ln(PIM stock)")+
  ylab(label =element_blank())+
  geom_vline(xintercept = c(1978,1991),linetype="dashed")+
  theme_bw()
```


# Cross sectional analysis

\begin{table}[htpb]
\begin{tabular}{|c|cc|}
\hline
\multirow{2}{*}{Explanation variables}  & \multicolumn{2}{c|}{Dependent variables}  \\
\cline{2-3}
& $\Delta ln(\frac{L}{F})$ & $\Delta ln(F)$\\
\hline
\multirow{2}{*}{$\Delta ln(\frac{PIM\ stock}{F})$} & $0.17^{***}$ & $-0.33^{***}$\\
 & (0.050) & (0.075) \\
 \hline
\multirow{2}{*}{$\Delta(\frac{IWM\ stock}{F})$} &$0.16^{***}$ & $-0.31^{***}$\\
 &(0.049) & (0.074) \\
 \hline
\multirow{2}{*}{$\Delta ln(\frac{PIM\ stock}{L})$} & $0.14^{*}$ & $-0.34^{***}$ \\
 &(0.069) & (0.10)\\
 \hline
\multirow{2}{*}{$\Delta ln(\frac{IWM\ stock}{L})$} & $0.14^{*}$ & $-0.32^{***}$\\
 &(0.066) & (0.10)\\
 \hline
\multirow{2}{*}{$\Delta ln(PIM\ stock)$} & $0.17^{*}$ & $-0.26^{*}$ \\
 &(0.080) & (0.14)\\
 \hline
\multirow{2}{*}{$\Delta ln(IWM\ stock)$} & $0.16^{*}$ & $-0.25^{*}$\\
 &(0.077) & (0.13)\\
 \hline
 \hline
 Obs. & 16 & 16\\
 \hline
 \end{tabular}\\
Note: $^{***}p<0.01,\ ^{**}p<0.05,\ ^{*}p<0.1$.\\
F denotes the numbers of firms, L denotes the employment.
\end{table}

# Cross sectional analysis

Changing $\iota_{ai}$ from "the average sales value from 1978 to 2018"   
to "the average value from 1978 to 1991" does not affect the result so much.

\begin{table}[htpb]
\begin{tabular}{|c|cc|}
\hline
\multirow{2}{*}{Explanation variables}  & \multicolumn{2}{c|}{Dependent variables}  \\
\cline{2-3}
& $\Delta ln(\frac{L}{F})$ & $\Delta ln(F)$\\
\hline
\multirow{2}{*}{$\Delta ln(\frac{PIM\ stock}{F})$} & $0.16^{***}$ & $-0.32^{***}$\\
 & (0.047) & (0.068) \\
 \hline
\multirow{2}{*}{$\Delta(\frac{IWM\ stock}{F})$} &$0.17^{***}$ & $-0.34^{***}$\\
 &(0.048) & (0.069) \\
 \hline
\multirow{2}{*}{$\Delta ln(\frac{PIM\ stock}{L})$} & $0.15^{**}$ & $-0.34^{***}$ \\
 &(0.064) & (0.091)\\
 \hline
\multirow{2}{*}{$\Delta ln(\frac{IWM\ stock}{L})$} & $0.15^{**}$ & $-0.36^{***}$\\
 &(0.067) & (0.093)\\
 \hline
\multirow{2}{*}{$\Delta ln(PIM\ stock)$} & $0.17^{**}$ & $-0.29^{**}$ \\
 &(0.076) & (0.13)\\
 \hline
\multirow{2}{*}{$\Delta ln(IWM\ stock)$} & $0.18^{**}$ & $-0.31^{*}$\\
 &(0.079) & (0.14)\\
 \hline
 \end{tabular}\\
\end{table}

# Panel Analysis

Adachi et al.(2020) and Arai et al.(2021) indicates we can use the robot price indicator as an instrumental variable for the robot stock.
While their data covers 1980's, my data only covers 1994 to 2018.  
\medskip  
\begin{center}
Controlled with \it{Global Control} and \it{ICT Stock},  
\end{center}

|  Period  |   Weight  | Weak IV F-stat
| :-: | :-: | :-:|
| 1978-2018 | 1978-1980 | 35.85
| 1994-2018 | 1991-1993 | 4.38
| 1994-2018 | 1978-1980 | 0.64
| 1980-1989 | 1978-1980 | 29.04
| 1980-1989 | 1978-1980 | 26.29

 - _Global Control_  is import value plus export value  
 - _ICT stock_ is Information and Communication Technology stock in JIP database.  
 
# Price as an IV

Changing methods to making robot stocks and changing weights have not improved Weak IV F statics so far.  
The value do not even exceed 6.  

# 