---
title: "Progress So far"
author: "Kosuke Arai"
date: "10/8/2021"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("rat.R")
dat <- read_csv("masterdata.csv") %>% rename(sales=investment)
```

## Price as IV

AKS and Fujiwara, Shirota and Arai indicates we can use price as an IV for stock.
It seems not for my sample period.
i.e. Weak IV test indicates price is an weak instrument. 
Different from AKS but same with FSA, I set the deprecation rate 0.18, life length infinity
so that the robot stock of industry i in time t,$K_{i,t}=R_{i,t}+(1-0.18)K_{i,t-1}$


## Weak IV test

Controlled with \it{Global Control} and \it{ICT Stock},  

|  Period  |   Weight  | F-stat
| :-: | :-: | :-:|
| 1978-2018 | 1978-1980 | 29.59
| 1994-2018 | 1990-1993 | 1.915
| 1994-2018 | 1978-1980 | 3.816
| 1978-1989 | 1980-1989 | 25.35


$\rightarrow$ The main driver of the relationship between price and stock is 1980's.
 
 - _Global Control_  is import value plus export value  
 - _ICT stock_  is ICT stock measured by the data JIP.  
 

## Price as IV

On the other hand, AKS set the deprecation rate 0 and life length 12 years (same with International Federation of Robotics,IFR)  
so that the robot stock of industry i in time t;
\[
K_{i,t}=\sum_{\tau = t-11}^{t} R_{i,\tau}
\]


## Weak IV test

Controlled with \it{Global Control} and \it{ICT Stock},  

|  Period  |   Weight  | F-stat
| :-: | :-: | :-:|
| 1978-2018 | 1978-1980 | 23.33
| 1994-2018 | 1990-1993 | 0.264
| 1994-2018 | 1978-1980 | 2.96
| 1978-1989 | 1980-1989 | 33.21


$\rightarrow$ The main driver of the relationship between price and stock is 1980's.
 
 - _Global Control_  is import value plus export value  
 - _ICT stock_  is ICT stock measured by the data JIP.  
 
## Robot Stocks

```{r,echo=FALSE}
head(dat)
```